---
title: "Workflow to create a SIM of population to retails flow in UK high streets"
author: azanchetta@turing.ac.uk
date: 20/09/2021
output: rmarkdown::github_document
---

Bibliography:
Lovelace, R., Birkin, M., Cross, P., Clarke, M. (2016). ‘From Big Noise to Big Data: Toward the Verification of Large Data sets for Understanding Regional Retail Flows’, Geographical Analysis 48, 59–81

Wilson, A.G. (1971). ‘A Family of Spatial Interaction Models, and Associated Developments’. Environment and Planning, 3, 1-32

CDRC (2021). Retail centre boundaries. Available at: https://data.cdrc.ac.uk/dataset/retail-centre-boundaries.

Data:
UK Office for National Statistics (ONS): the demographic data (population characteristics, occupation) at LSOA levels from the Census 2011 data and the geographic data from the Open Geography portal.
The list of UK retail centres, with their boundaries, is provided by the University of Liverpool and is available at CDRC (2021).


Open questions:
-	At which level to run the analysis: national scale or regional/LAD
-	Dimension of attractiveness values
-	Calibration of the model

Workflow:
-	Generate centroids for the population (origins) and the retail centres (destinations)
-	Generate the origin-destination matrix and the other variables necessary to run the model
-	Run the model on the student population, then perform calibration
-	Run the model on different scenarios for different groups of individuals and perform analysis of the results




The [R plugin](https://www.jetbrains.com/help/pycharm/r-plugin-support.html) for IntelliJ-based IDEs provides
handy capabilities to work with the [R Markdown](https://www.jetbrains.com/help/pycharm/r-markdown.html) files.
To [add](https://www.jetbrains.com/help/pycharm/r-markdown.html#add-code-chunk) a new R chunk,
position the caret at any line or the code chunk, then click "+".

The code chunk appears:
```{r}
```

Type any R code in the chunk, for example:
```{r}
mycars <- within(mtcars, { cyl <- ordered(cyl) })
mycars
```

Now, click the **Run** button on the chunk toolbar to [execute](https://www.jetbrains.com/help/pycharm/r-markdown.html#run-r-code) the chunk code. The result should be placed under the chunk.
Click the **Knit and Open Document** to built and preview an output.